Weighted Model Counting Without Parameter Variables

### 2021-02-28 doc/paper3/box.tex
Writing
Lots of writing

% Created by tikzDevice version 0.12.3.1 on 2021-02-23 15:58:55
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (346.90,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (346.90,144.54);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 30.69) rectangle (275.96,139.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 30.69) rectangle (275.96,139.04);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 54.03) --
	(275.96, 54.03);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 91.24) --
	(275.96, 91.24);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,128.46) --
	(275.96,128.46);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 35.42) --
	(275.96, 35.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 72.64) --
	(275.96, 72.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,109.85) --
	(275.96,109.85);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.15, 30.69) --
	( 74.15,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (130.20, 30.69) --
	(130.20,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (186.26, 30.69) --
	(186.26,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (242.32, 30.69) --
	(242.32,139.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.63,115.66) -- ( 63.63,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 63.63, 41.94) -- ( 63.63, 35.91);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 54.17,115.66) --
	( 54.17, 41.94) --
	( 73.09, 41.94) --
	( 73.09,115.66) --
	( 54.17,115.66) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 54.17, 63.32) -- ( 73.09, 63.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.66, 65.49) -- ( 84.66,104.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.66, 38.03) -- ( 84.66, 35.61);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 75.20, 65.49) --
	( 75.20, 38.03) --
	( 94.12, 38.03) --
	( 94.12, 65.49) --
	( 75.20, 65.49) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 75.20, 42.42) -- ( 94.12, 42.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.69,119.81) -- (119.69,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.69, 43.24) -- (119.69, 36.02);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (110.23,119.81) --
	(110.23, 43.24) --
	(129.15, 43.24) --
	(129.15,119.81) --
	(110.23,119.81) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (110.23, 64.90) -- (129.15, 64.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.71,104.94) -- (140.71,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.71, 40.63) -- (140.71, 35.85);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (131.26,104.94) --
	(131.26, 40.63) --
	(150.17, 40.63) --
	(150.17,104.94) --
	(131.26,104.94) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (131.26, 50.31) -- (150.17, 50.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.75,119.86) -- (175.75,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (175.75, 43.24) -- (175.75, 36.02);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (166.29,119.86) --
	(166.29, 43.24) --
	(185.21, 43.24) --
	(185.21,119.86) --
	(166.29,119.86) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (166.29, 64.90) -- (185.21, 64.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (196.77,104.94) -- (196.77,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (196.77, 40.63) -- (196.77, 35.85);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (187.31,104.94) --
	(187.31, 40.63) --
	(206.23, 40.63) --
	(206.23,104.94) --
	(187.31,104.94) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (187.31, 50.31) -- (206.23, 50.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.81,107.47) -- (231.81,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.81, 40.63) -- (231.81, 35.83);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (222.35,107.47) --
	(222.35, 40.63) --
	(241.27, 40.63) --
	(241.27,107.47) --
	(222.35,107.47) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (222.35, 55.32) -- (241.27, 55.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.83, 69.18) -- (252.83,104.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.83, 38.03) -- (252.83, 35.61);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (243.37, 69.18) --
	(243.37, 38.03) --
	(262.29, 38.03) --
	(262.29, 69.18) --
	(243.37, 69.18) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (243.37, 42.87) -- (262.29, 42.87);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 30.69) rectangle (275.96,139.04);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 32.39) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 69.61) {2000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,106.82) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 35.42) --
	( 40.51, 35.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 72.64) --
	( 40.51, 72.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,109.85) --
	( 40.51,109.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.15, 27.94) --
	( 74.15, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (130.20, 27.94) --
	(130.20, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (186.26, 27.94) --
	(186.26, 30.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] (242.32, 27.94) --
	(242.32, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 74.15, 19.68) {\texttt{bklm16}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (130.20, 19.68) {\texttt{cd05}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (186.26, 19.68) {\texttt{cd06}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (242.32, 19.68) {\texttt{d02}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 84.86) {Variables};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (286.96, 57.30) rectangle (341.40,112.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (292.46, 77.26) rectangle (306.91, 91.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 78.70) --
	(299.68, 80.87);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 88.10) --
	(299.68, 90.26);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (294.26, 80.87) rectangle (305.10, 88.10);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.26, 84.48) --
	(305.10, 84.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (292.46, 62.80) rectangle (306.91, 77.26);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 64.25) --
	(299.68, 66.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.68, 73.64) --
	(299.68, 75.81);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (294.26, 66.42) rectangle (305.10, 73.64);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.26, 70.03) --
	(305.10, 70.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (312.41, 81.45) {before};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (346.90,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (312.41, 67.00) {after};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-02-28 16:52:48
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (173.45,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (173.45,144.54);
\end{scope}
\begin{scope}
\path[clip] ( 40.51, 33.38) rectangle (167.95,139.04);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 40.51, 33.38) rectangle (167.95,139.04);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 56.14) --
	(167.95, 56.14);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51, 92.43) --
	(167.95, 92.43);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 40.51,128.72) --
	(167.95,128.72);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 38.00) --
	(167.95, 38.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51, 74.29) --
	(167.95, 74.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 40.51,110.58) --
	(167.95,110.58);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 55.21, 33.38) --
	( 55.21,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 79.72, 33.38) --
	( 79.72,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (104.23, 33.38) --
	(104.23,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (128.74, 33.38) --
	(128.74,139.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (153.24, 33.38) --
	(153.24,139.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 50.62,116.24) -- ( 50.62,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 50.62, 44.35) -- ( 50.62, 38.47);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 46.48,116.24) --
	( 46.48, 44.35) --
	( 54.75, 44.35) --
	( 54.75,116.24) --
	( 46.48,116.24) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.48, 65.20) -- ( 54.75, 65.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.81, 67.32) -- ( 59.81,104.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.81, 40.54) -- ( 59.81, 38.18);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 55.67, 67.32) --
	( 55.67, 40.54) --
	( 63.95, 40.54) --
	( 63.95, 67.32) --
	( 55.67, 67.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 55.67, 44.82) -- ( 63.95, 44.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.13,120.28) -- ( 75.13,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.13, 45.62) -- ( 75.13, 38.58);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 70.99,120.28) --
	( 70.99, 45.62) --
	( 79.26, 45.62) --
	( 79.26,120.28) --
	( 70.99,120.28) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.99, 66.74) -- ( 79.26, 66.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.32,105.79) -- ( 84.32,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.32, 43.08) -- ( 84.32, 38.42);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 80.18,105.79) --
	( 80.18, 43.08) --
	( 88.45, 43.08) --
	( 88.45,105.79) --
	( 80.18,105.79) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 80.18, 52.51) -- ( 88.45, 52.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.63,120.34) -- ( 99.63,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.63, 45.62) -- ( 99.63, 38.58);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 95.50,120.34) --
	( 95.50, 45.62) --
	(103.77, 45.62) --
	(103.77,120.34) --
	( 95.50,120.34) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.50, 66.74) -- (103.77, 66.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.82,105.79) -- (108.82,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.82, 43.08) -- (108.82, 38.42);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (104.69,105.79) --
	(104.69, 43.08) --
	(112.96, 43.08) --
	(112.96,105.79) --
	(104.69,105.79) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (104.69, 52.51) -- (112.96, 52.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (124.14,108.25) -- (124.14,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (124.14, 43.08) -- (124.14, 38.40);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (120.01,108.25) --
	(120.01, 43.08) --
	(128.28, 43.08) --
	(128.28,108.25) --
	(120.01,108.25) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.01, 57.40) -- (128.28, 57.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (133.33, 70.91) -- (133.33,104.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (133.33, 40.54) -- (133.33, 38.18);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (129.20, 70.91) --
	(129.20, 40.54) --
	(137.47, 40.54) --
	(137.47, 70.91) --
	(129.20, 70.91) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (129.20, 45.26) -- (137.47, 45.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.24, 89.69) -- (153.24,144.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.24, 41.81) -- (153.24, 38.29);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (144.97, 89.69) --
	(144.97, 41.81) --
	(161.51, 41.81) --
	(161.51, 89.69) --
	(144.97, 89.69) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (144.97, 53.85) -- (161.51, 53.85);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.51, 33.38) rectangle (167.95,139.04);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 34.97) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56, 71.26) {2000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 35.56,107.55) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 38.00) --
	( 40.51, 38.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76, 74.29) --
	( 40.51, 74.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 37.76,110.58) --
	( 40.51,110.58);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 55.21, 30.63) --
	( 55.21, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 79.72, 30.63) --
	( 79.72, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (104.23, 30.63) --
	(104.23, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (128.74, 30.63) --
	(128.74, 33.38);

\path[draw=drawColor,line width= 0.3pt,line join=round] (153.24, 30.63) --
	(153.24, 33.38);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 55.21, 22.37) {\texttt{bklm16}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 79.72, 22.37) {\texttt{cd05}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (104.23, 22.37) {\texttt{cd06}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (128.74, 22.37) {\texttt{d02}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (153.24, 22.37) {\texttt{sbk05}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 86.21) {Variables};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 58.10,  5.50) rectangle (150.36, -2.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 63.60,  5.50) rectangle ( 78.05, 19.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 70.83,  6.95) --
	( 70.83,  9.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 70.83, 16.34) --
	( 70.83, 18.51);
\definecolor{fillColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 65.41,  9.11) rectangle ( 76.25, 16.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 65.41, 12.73) --
	( 76.25, 12.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (112.54,  5.50) rectangle (126.99, 19.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (119.77,  6.95) --
	(119.77,  9.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (119.77, 16.34) --
	(119.77, 18.51);
\definecolor{fillColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (114.35,  9.11) rectangle (125.19, 16.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (114.35, 12.73) --
	(125.19, 12.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 83.55,  9.70) {before};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (132.49,  9.70) {after};
\end{scope}
\end{tikzpicture}
